Title

### 2013-03-30 inc/model_results/shapes/shapes.tex
added cc notices to the tops of several files
flattened model_results section headings, removing free-space versus forced
began correction on model_results sections

\subsection{Trends for Initial Shapes} \label{sec:initial_shapes}

The initial `space-time' eccentricity \ref{eq:define_xi}, $\xi ( 0 ) = v_{\smallzero} \tau / w $ , of the photo-generated electron pulse plays a major role in the bunch propagation dynamics, particularly when space-charge effects dominate.
\ref{fig:compare_shape} illustrates the typical dynamics of initially spherical ($ \sigma_{ \smallT }(0) = \sigma_{z} ( 0 ) $), oblate or `disk-like' ($ \sigma_{ \smallT } ( 0 ) > \sigma_{ z } ( 0 ) $), and prolate or `cigar-like' ($ \sigma_{ z } ( 0 ) > \sigma_{ \smallT } ( 0 ) $) pulses.
%TODO rewrite using w?
For simplicity, and unlike most simulations in this paper, the pulses in this simulation are not calculated from laser and photocathode parameters, but are rather defined directly.
%TODO should I remove this? Should I just specify the creation types on each instance?
The initial bunch dimensions are given by the ellipticities $ \xi(0) = \{ 1/3 , 1 , 3 \} $ while in each case the product of the initial HW1/eM bunch widths $w_{\smallT}^2 w_z = $ 1mm$^3$.
Since the initial pulse volume is consistent between all runs, initial peak pulse charge density is six orders of magnitude greater in \ref{fig:compare_shape}\subref{fig:compare_shape_N1e6} ($ N = 10^{6} $ electrons in the bunch) than in \ref{fig:compare_shape}\subref{fig:compare_shape_N1} ($ N = 10^{0} $).
The pulse velocity is $ v_{\smallzero} \approx c/3 $, i.e. a DC photogun with $V = 30\text{kV} $.

\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:compare_shape_N1}
    \input{shapes_N1}
  }
  \\
  \subfloat[][]{
    \label{fig:compare_shape_N1e6}
    \input{shapes_N1e6}
  }
  \caption[AG simulation of free-space pulse expansion]{
    Transverse (solid) and longitudinal (dashed) dynamics of three example pulses for three length/width ratios ($\xi$). 
    The red lines represent a oblate pulse (a ``pancake'') with $\xi=1/3$, green lines for a spherical pulse with $\xi=1$, and blue for an prolate pulse (a ``cigar'') having $\xi=3$.
    The pulses shown in \ref{fig:compare_shape_N1} all have total charge $N=1$, while in \ref{fig:compare_shape_N1e6} the pulses have $N=10^6$.
  }
  \label{fig:compare_shape}
\end{figure}

>>>>

%This work is licensed under the Creative Commons Attribution-NonCommercial-NoDerivs 3.0 United States License. To view a copy of this license, visit http://creativecommons.org/licenses/by-nc-nd/3.0/us/ or send a letter to Creative Commons, 444 Castro Street, Suite 900, Mountain View, California, 94041, USA.

\section{Effect of Pulse Eccentricity on Dynamics} \label{sec:initial_shapes}

The initial `space-time' eccentricity (defined in \ref{eq:define_xi}), $\xi ( 0 ) = v_{\smallzero} \tau / w $ , of the photo-generated electron pulse plays a major role in the bunch propagation dynamics, particularly when space-charge effects dominate.
\ref{fig:compare_shape} illustrates the typical dynamics of initially spherical ($ \sigma_{ \smallT }(0) = \sigma_{z} ( 0 ) $), oblate or `disk-like' ($ \sigma_{ \smallT } ( 0 ) > \sigma_{ z } ( 0 ) $), and prolate or `cigar-like' ($ \sigma_{ \smallT } ( 0 ) < \sigma_{ z } ( 0 ) $) pulses.
%TODO rewrite using w?
This simulation uses the idealized pulse conditions described above, where the initial bunch dimensions are given by the ellipticities $ \xi(0) = \{ 1/3 , 1 , 3 \} $ and in each case the product of the initial HW1/eM bunch widths $w_{\smallT}^2 w_z = $ 1mm$^3$.
Pulses used in \ref{fig:compare_shape}\subref{fig:compare_shape_N1} have just one electron per pulse (i.e. $ N = 10^{0} $), while \ref{fig:compare_shape}\subref{fig:compare_shape_N1e6} have a much higher $ N = 10^{6} $ electrons in the bunch.
Since the initial pulse volume is consistent between all runs, initial peak pulse charge density is six orders of magnitude greater in \ref{fig:compare_shape}\subref{fig:compare_shape_N1e6} than in \ref{fig:compare_shape}\subref{fig:compare_shape_N1}.
The pulse velocity is $ v_{\smallzero} \approx c/3 $, i.e. a DC photogun with $V = 30\text{kV} $.

\begin{figure}
  \centering
  \subfloat[][]{
    \label{fig:compare_shape_N1}
    \input{shapes_N1}
  }
  \\
  \subfloat[][]{
    \label{fig:compare_shape_N1e6}
    \input{shapes_N1e6}
  }
  \caption[AG simulation of free-space pulse expansion]{
    Transverse (solid) and longitudinal (dashed) dynamics of three example pulses for three length/width ratios ($\xi$). 
    The red lines represent a oblate pulse (a ``pancake'') with $\xi=1/3$, green lines for a spherical pulse with $\xi=1$, and blue for an prolate pulse (a ``cigar'') having $\xi=3$.
    The pulses shown in \subref{fig:compare_shape_N1} all have total charge $N=1$, while in \subref{fig:compare_shape_N1e6} the pulses have $N=10^6$.
  }
  \label{fig:compare_shape}
\end{figure}
